Forecasting the 2024 U.S. Presidential Election: A Poll-of-Polls Approach for Predicting the Outcome

### 2024-11-04 paper/paper.qmd
2

library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)
library(rstanarm)
library(maps)
data <- read_parquet("../data/02-analysis_data/cleaned_president_polls.parquet")
```

>>>>

# Load required libraries
library(tidyverse)
library(ggplot2)
library(MASS)
library(dplyr)
library(rstanarm)
library(maps)
library(arrow)  # Ensure arrow is loaded to use read_parquet()

# Read the dataset using arrow
data <- read_parquet("../data/02-analysis_data/cleaned_president_polls.parquet")
